---
title: "HW 2"
author: "Bryan Mui - UID 506021334"
date: "2025-01-29"
output: pdf_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, echo=FALSE, inlude=FALSE}
library(tidyverse)
source("./506021334_stats102a_hw2.R")
set.seed(506021334)
```

# Problem 1

## 1a, create a simulated dataset

simulate():  \
generate 100 UIDs starting from 100000000 \
Create homework 1-5 and quiz 1-7, using floor and runif to get a randomized value between 1-100 \


```{r, 1a_fin}
gradebook <- simulate_data()
# arrange by increasing UID 
gradebook <- gradebook %>%
  arrange(UID)
head(gradebook)
```

## 1b) write R code in the R markdown file to randomly replace 10% of the values in HW1, HW5, and Quiz3 with NA values. Use is.na() and sum() to display the results

Algorithm:  \
generate random indices as a logical vector(replace or not replace)  \
subset the data and replace TRUE index with NA \

```{r, 1b_fin}
gradebook$Homework_1 <- replace_10_percent(gradebook$Homework_1)
gradebook$Homework_5 <- replace_10_percent(gradebook$Homework_5)
gradebook$Quiz_3 <- replace_10_percent(gradebook$Quiz_3)

# summary of the replacements:
gradebook %>%
  select(Homework_1, Homework_5, Quiz_3) %>%
  summarise(sum(is.na(.)))

cat("30 data points should be replaced as NA.")
```

## 1c) Write a function messy_impute() that imputes using missing values in the gradebook 

## 1d) Please select one student whose quiz or homework has undergone imputation to showcase your function

## 1e) Write R code using the main functions in the tidyr package to convert the gradebook into the tidy format

```{r}
# Convert gradebook to tidy 
gradebook_tidy <- gradebook %>%
  pivot_longer(
    cols = -UID,
    names_to = "Assesment",
    values_to = "Score"
  ) %>%
  separate(
    col = Assesment,
    into = c("Assesment", "Number"),
    sep = "_"
  ) %>%
  mutate(Number=as.numeric(.$Number))
head(gradebook_tidy, 15)
```

## 1f) Write a function tidy impute() that imputes missing values in gradebook tidy object

## 1g) Please use the cases you select from (d) to demonstrate your function in the R markdown
