---
title: "HW 2"
author: "Bryan Mui - UID 506021334"
date: "2025-01-29"
output: pdf_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, echo=FALSE}
library(tidyverse)
source("./506021334_stats102a_hw2.R")
set.seed(506021334)
```

# Problem 1

## 1a, create a simulated dataset

simulate():  \
generate 100 UIDs starting from 100000000 \
Create homework 1-5 and quiz 1-7, using floor and runif to get a randomized value between 1-100 \


```{r, 1a}
data <- simulate_data()
head(data)
```

## 1b) write R code in the R markdown file to randomly replace 10% of the values in HW1, HW5, and Quiz3 with NA values. Use is.na() and sum() to display the results

Algorithm:  \
generate random indices as a logical vector(replace or not replace)  \
subset the data and replace TRUE index with NA \

```{r, 1b}
data$Homework1 <- replace_10_percent(data$Homework1)
data$Homework5 <- replace_10_percent(data$Homework5)
data$Quiz3 <- replace_10_percent(data$Quiz3)

# summary of the replacements:
data %>%
  select(Homework1, Homework5, Quiz3) %>%
  summarise(sum(is.na(.)))

# 30 data points total were replaced as NA
```

## 1c) Write a function messy_impute() that imputes using missing values in the gradebook 

