---
title: "HW 3"
author: "Bryan Mui - UID 506021334"
date: "2025-02-12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Things to ask \n
* ask if part 1 should be in the R script
* ask about 1d 


## Section 1: Cook's relational data

library and read csv files: 

```{r lib_and_read_csv, warning=FALSE, echo=FALSE}
library(tidyverse)
source("./506021334_stats102a_hw3.R")
recipe <- read_csv("recipe.csv")
ingredient <- read_csv("ingredient.csv")
stock <- read_csv("stock.csv")
food_item <- read_csv("food_item.csv")
```

### 1a) Write R code to return the types of food and the total calories for each type to make a turkey burger from the recipe.

```{r 1_1a_fin}
a1
```

### 1b) Write R code to return all recipes containing both bread and tomato products with their weights on these two ingredients.

```{r 1_1b_fin}
b1
```

### 1c) Write R code to return the total calories of the beef and turkey burgers.

```{r 1_1c_fin}
c1
```

### 1d) Write R code to return all vegetable items sold at either ‘W-Mart’ or ‘Food Warehouse’ and display which shop offers the lowest price for each item. 

```{r 1_1d_fin}
d1
```


### 1e) Write R code to return the recipes with the total calories that contain “Wheat product”.

```{r 1_1e_fin}
e1
```


## Section 2: Regular Expression Exercises 

Find names.txt and write regex patterns to answer following questions.

### 2a) Find all usernames that contain at least one numeric character.

```{r 2_1a}
txt <- readLines("./names.txt")
txt
```

