---
title: "HW 3"
author: "Bryan Mui - UID 506021334"
date: "2025-02-12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Things to ask \n
* 1a, what is the correct kind of output
* 1b, how to do


## Section 1: Cook's relational data

library and read csv files: 

```{r lib_and_read_csv, warning=FALSE, echo=FALSE}
library(tidyverse)
source("./506021334_stats102a_hw3.R")
recipe <- read_csv("recipe.csv")
ingredient <- read_csv("ingredient.csv")
stock <- read_csv("stock.csv")
food_item <- read_csv("food_item.csv")
```

### 1a) Write R code to return the types of food and the total calories for each type to make a turkey burger from the recipe.

```{r 1_1a_fin}
a1
```

### 1b) Write R code to return all recipes containing both bread and tomato products with their weights on these two ingredients.

```{r 1_1b_fin}
b1
```

### 1c) Write R code to return the total calories of the beef and turkey burgers.

```{r 1_1c_fin}
c1
```

### 1d) Write R code to return all vegetable items sold at either ‘W-Mart’ or ‘Food Warehouse’ and display which shop offers the lowest price for each item. 

```{r 1_1d_fin}
d1
```


### 1e) Write R code to return the recipes with the total calories that contain “Wheat product”.

```{r 1_1e_fin}
e1
```


## Section 2: Regular Expression Exercises 

### Part 1: Find names.txt and write regex patterns to answer following questions.

### 1a) Find all usernames that contain at least one numeric character.

```{r read_txt}
txt <- readLines("./names.txt")
txt
```


```{r 2_1a}
# remember to store in R file!!!!!!!!!!!!!!!!!!!
pat_1_a <- "\\d"
str_view(txt, pat_1_a)
```

### 1b) Find all usernames that are exactly four characters long and consist only of alphabetic characters.

```{r 2_1b}
pat_1_b <- "\\A[[:alpha:]]{4}\\Z"
str_view(txt, pat_1_b)
```
### 1c) Find all usernames following the conventional name format, where the given name precedes the family name, with optional additional names in-between. Each name segment is separated by a single white space and should begin with an uppercase letter followed by one or more lowercase letters. Note that intermediate names should also start with an uppercase letter followed by zero or more lowercase letters.

```{r 2_1c}
pat_1_c <- "\\A[A-Z][a-z]+ [[:alpha:]]*[ ]*[A-Z][a-z]+\\Z"
str_view(txt, pat_1_c)
```

### Part 2: Find cards.txt and write the regex patterns to identify all the valid card numbers with the correct formatting rules:
  + A Master card number begins with a 5 and it is exactly 16 digits long.
  + A Visa card number begins with a 4 and it is between 13 and 16 digits long
  
```{r read_cards}
cards <- readLines("./cards.txt")
cards
```

### 2a) Write a regex pattern to match valid Master card number and print all the valid numbers, grouped into sets of 4 separated by a single space.

```{r 2_2a}
# Valid master card numbers 
pat_2_a <- "^5[[:digit:]]{3}[ ]*([[:digit:]]{4}[ ]*){3}$"
str_view(cards, pat_2_a)
```

### 2b) Write a regex pattern to match valid Visa card number and print all the valid numbers, grouped into sets of 4 separated by a single space.

```{r 2_2b}
# Valid Visa card numbers
pat_2_b <- "^4[[:digit:]]{3}[ ]*([[:digit:]]{4}[ ]*){2}[[:digit:]]{1,4}$"
str_view(cards, pat_2_b)
```


### Part 3: Find the passwords.txt and write regex patterns to answer the following questions.

```{r read_passwords}
passwords <- readLines("./passwords.txt")
passwords
```

### 3a) Write a regex pattern to identify the passwords that satisfies the requirements below.
  + Minimum 8 characters
  + Must contain at least one letter
  + Must contain at least one digit

```{r 3_a}
# "(?=\\d{1,8})(?=[[:alpha:]]{1,8}).{8,}"
pat_3_a <- "[0-9]+?"
str_view(passwords, pat_3_a)
```

  
### 3b) Write a regex pattern to identify the passwords that satisfies the requirements below
+ Minimum 8 characters
+ Must contain at least one uppercase character
+ Must contain at least one lowercase character
+ Must contain at least one digit
+ Must contain at least one punctuation character

```{r 3_b}

```

### Part 4: Please load wordlists.RData to R and write regular expression patterns which will match all of the values in x and none of the values in y.

### a) Ranges

```{r read_wordlists}
load("./wordlists.RData")
```

```{r 4_a}
wordlists$Ranges
pat_4_a <- "a"
str_view(wordlists$Ranges$x, pat_4_a)
cat("-------------BREAK---------------\n")
str_view(wordlists$Ranges$y, pat_4_a)
```


### b) Backrefs

```{r 4_b}
wordlists$Backrefs
```

### c) Prime

```{r 4_c}
wordlists$Prime  
```




