---
title: "HW 3"
author: "Bryan Mui - UID 506021334"
date: "2025-02-12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Things to ask \n
* ask if part 1 should be in the R script
* ask about 1d 


## Section 1: Cook's relational data

library and read csv files: 

```{r lib_and_read_csv, warning=FALSE, echo=FALSE}
library(tidyverse)
recipe <- read_csv("recipe.csv")
ingredient <- read_csv("ingredient.csv")
stock <- read_csv("stock.csv")
food_item <- read_csv("food_item.csv")
```

### 1a) Write R code to return the types of food and the total calories for each type to make a turkey burger from the recipe.

```{r 1a_fin}
# need to output calories, food type for turkey burger 
a1 <- recipe %>% 
  transmute(recipe=name) %>% 
  left_join(ingredient, by="recipe") %>% 
  rename(item=food_item) %>%
  left_join(food_item, by="item") %>% 
  filter(recipe=="Turkey Burger") %>%
  select(recipe, item, type, calories)
a1
```

### 1b) Write R code to return all recipes containing both bread and tomato products with their weights on these two ingredients.

```{r 1b_fin}
b1 <- ingredient %>%
  group_by(recipe) %>%
  filter(food_item=="Tomato" | food_item=="Bread" | food_item=="Tomato Sauce") %>%
  filter(any(food_item=="Bread")) %>%
  summarize(sum_bread_and_tomato=sum(`weight (oz)`))
b1
```

### 1c) Write R code to return the total calories of the beef and turkey burgers.

```{r 1c_fin}
c1 <- ingredient %>%
  rename(item=food_item) %>%
  right_join(food_item, by="item") %>%
  rename(kcal_per_oz=calories) %>% 
  mutate(kcal_total=kcal_per_oz*`weight (oz)`) %>%
  group_by(recipe) %>% 
  summarize(total_calories=sum(kcal_total)) %>%
  filter(recipe=="Beef Burger" | recipe=="Turkey Burger")
c1
```

### 1d) Write R code to return all vegetable items sold at either ‘W-Mart’ or ‘Food Warehouse’ and display which shop offers the lowest price for each item. 

```{r 1d}
d1 <- food_item %>%
  rename(food_item=item) %>%
  left_join(stock, by="food_item") %>%
  rename(price=`price (US dollars per lb)`) %>%
  filter(type=="Vegetables", shop=="W-Mart" | shop=="Food warehouse")
d1
```


### 1e) Write R code to return the recipes with the total calories that contain “Wheat product”.

```{r 1e_fin}
e1 <- ingredient %>% 
  rename(item=food_item) %>%
  left_join(food_item, by="item") %>%
  group_by(recipe) %>%
  filter(any(type=="Wheat product")) %>% 
  mutate(kcal_calc=(`weight (oz)` * calories)) %>%
  summarize(total_kcal=sum(kcal_calc))
e1
```


## Section 2: Regular Expression Exercises 

### Find names.txt and write regex patterns to answer following questions.

```{r}
txt <- readLines("./names.txt")
```

